
\cvsection{SKILLS}
\begin{itemize}
  \item \textbf{Programming}: python, javascript, C\#, java, R
  \item \textbf{Data Analysis}: pandas, sklearn, tensorflow, pytorch
  \item \textbf{Data Visualisation}: matplotlib, d3, plotly
  \item \textbf{Backend}: django, flask, nodeJS (express)
  \item \textbf{Frontend}: typescript, react, threeJS, tensorflowJS
  \item \textbf{Hybrid}: electronJS, react native
  \item \textbf{DB}: postgreSQL, mongoDB, elasticsearch
  \item \textbf{DevOps}: docker, git, vagrant, ssh
  \item \textbf{Bioinformatics}: clustalo, rdkit, biopython, blast, hmmer, cobra
\end{itemize}


\cvsection{LANGUAGES}
\cvskill{English, French, Spanish}{5}
\cvskill{German}{2}


\cvsection{Selected Projects}

\cvproject{Automated Dental Diagnosis with Deep Learning}
\begin{itemize}
  \item DL on 3D point clouds were used to segmentate teeth and gingiva from raw 3D data.
  \item Captures of mandible movements allowed for diagnosis of dental pathologies.
  \item Hybrid interface with animated 3D data used for presentation of results to main public.
\end{itemize}

\cvproject{Time Series Forecasting with Deep Learning}
\begin{itemize}
  \item Training of a DL model taking into account dynamic as well as static data allowed for automated forecast of time series coming from industrial environments.
\end{itemize}

\cvproject{Web Development Workshop in India}
\begin{itemize}
  \item I taught a 28-hour workshop about frontend web technologies: HTML, CSS, JS and React to students from Mahindra Ecole Centrale in Hyderabad, India.
\end{itemize}

\cvproject{Development and Deployment of a Scientific Full-Stack Web Application}
\begin{itemize}
	\item The application simplifies the retrieving and visualisation of biochemical data.
	\item Structured into SQL data from heterogenous sources (HPLC, mass spectrometry, gaz chromatography, ...) as well as DNA/Protein sequences.
\end{itemize}
\smallskip

\cvproject{Development of a Mass Spectrometry Data Analysis Pipeline.}
\begin{itemize}
	\item Tool is capable of detecting relevant features (Machine Learning) and identifying them comparing fragmentation spectra from raw data and \textit{in-silico} spectrum prediction.
\end{itemize}
\smallskip

\cvproject{Gene Research with Sequence Analysis.}
\begin{itemize}
	\item Several homologues with reinforced activity found in public and private databases using sequence comparison.
\end{itemize}
\smallskip

\cvproject{Chemoinformatics Reactions Database and an Enzyme Promiscuity Prediction tool.}
\begin{itemize}
	\item Biochemical reaction databases were fused with structural data from chemical databases. \textit{Atom-atom mapping} was computed in order to predict potential undesirable reactions.
\end{itemize}
\smallskip

\cvproject{Metabolic Network Modelling.}
\begin{itemize}
	\item Analysis of complex networks modelling the relations between genes, proteins, molecules and proteins inside the cell. Main conclusions led to publication of one patents.
\end{itemize}
\smallskip

% \cvproject{Transportation Network Modelling and Forecasting}
% \begin{itemize}
%     \item Creation and analysis of transportation networks holding geographical data for different transportation modes (train, cars, flights), as well as estimations of the current demand coming from polls and simulations.
% \end{itemize}
% \smallskip

% \cvproject{Macroeconomics Data Analysis and Forecasting.}
% \begin{itemize}
%     \item Publication of two documents in macroeconomics and public policies thanks to modelling, analysis and forecasting using macroeconomics data.
% \end{itemize}
